# Method
## Descriptions of Instructional Resources
We studied the words identified as requiring special instruction in the six resources named above. These materials were selected because of their popularity and because they address the development of early reading vocabulary, including the role of common words and the treatment of words with atypical pronunciations given their spellings. For curricula that specify words for several grades, we focused on those for 3rd grade students and younger. The @Dolch1936, @Fry1980, and @Kilpatrick2016 resources do not differentiate based on grade level, and so all words were included. Note that several of the resources studied here also teach decoding. We do not include words taught during decoding instruction in these analyses (e.g., the words "pat", "pick", and "pet" might be taught when teaching that the phoneme /p/ is associated with the letter "p") given that such instruction focuses on a different set of skills (related to pronouncing printed words exclusively based on the letter-sound patterns they contain). 

The @Dolch1936 and @Fry1980 materials are lists of words included in journal articles that described issues about learning to read and approaches to instruction. The lists, which are widely available on the internet, are utilized in research and in developing educational programs and activities, but are not curricula themselves. The remaining four (Fundations, Wonders, Fountas & Pinnell, and Kilpatrick) are instructional programs that include both lists of words and methods for teaching them. These four programs vary in how comprehensive they are as instructional tools. On one end, Wonders is a large-scale comprehensive reading curriculum and, at the other end, @Kilpatrick2016 is a supplementary instructional manual lacking many of the elements of more formal programs. 

### Dolch "Basic Sight Vocabulary"
@Dolch1936 presented “a basic sight vocabulary” of 220 words that he considered essential for reading development because they are “...‘tool’ words that are used in all writing, no matter what the subject.” (p.457). This set of what are often called “function” words was synthesized from several previous lists and supplemented with 95 common nouns. The “Dolch list” in wide circulation usually consists of these 315 words, although sometimes with minor changes. The list includes words with both typical and atypical spelling-sound correspondences. In words with typical correspondences, the pronunciation is one that is commonly associated with the spelling (e.g., "five", "paid"); in words with atypical correspondences, the pronunciation is less commonly associated with the spelling (e.g., "give", "said"). Dolch recommended that the words be printed on small cards that can be “flashed” before the pupil until they can be recognized “instantly and easily”, which is a method that leverages rote memorization. However he also noted that if the learner’s “sounding” (phonics) is weak additional instruction in that area may be required. 

### Fry "Instant Words"
@Fry1957 presented a set of 600 high frequency words based on word frequency counts available at the time [@Dolch1936; @Rinsland1945; @Thorndike1944] and additional  words that the author deemed common based on personal classroom experience. The words were organized into sets of 100, ordered by frequency, and within each set into four groups of 25. The goal was to allow a reading teacher access to groups of words, decreasing in frequency, in a quantity that could be easily managed in an instructional unit. @Fry1980 introduced “The New Instant Word List”, a revised version of the original set that included fewer words (300) chosen using newer frequency counts. We have utilized the Fry (1980) list in the analyses here. 

### Wilson's Fundations "Trick Words"
The Fundations curriculum incorporates extensive instruction about correspondences from spelling to sound and sound to spelling, using methods such as “tapping out” component sounds. The teacher’s manual notes that common (i.e., high frequency) words need to be recognized and spelled quickly even if the relevant spelling-sound correspondences have not yet be taught. These words include both “phonetically regular” and “phonetically irregular” words (i.e., words with typical and atypical mappings). The curriculum designates 193 words in K-3 as “trick” words that are to be memorized (see Table 1 for the number of words per grade level). These words have irregular spelling-sound mappings according to most theories. Students are told that these words “do not follow the ‘system’ of the language…[they] are phonetically irregular”. 

```{r fundations_counts_by_grade, echo=FALSE, warning=FALSE, message=FALSE}
tmp_fundations = all_lists %>% 
  filter(source == 'fundations') %>% 
  mutate(order = case_when(level == "k" ~ 1,
                           level == "g1" ~ 2,
                           level == "g2" ~ 3,
                           level == "g3" ~ 4)) %>% 
  mutate(level = str_remove(level, "g"),
         level = toupper(level),
         level = fct_reorder(level, order)) %>% 
  group_by(word) %>% 
  arrange(order) %>% 
  summarise(level = first(level)) %>%
  ungroup() %>% 
  group_by(level) %>%
  summarise(n = n()) %>% 
  select(Grade = level, Fundations = n)  %>% 
  rbind(all_lists %>% 
  filter(source == 'fundations') %>% 
  distinct(word) %>% 
  summarise(n = n()) %>% 
  mutate(Grade = "Total") %>% 
  rename(`Fundations` = n))

```

### Fountas & Pinnell's "Words to Know"
Fountas & Pinnell identify 312 “unique” words requiring special attention. The words are meant to be taught throughout the elementary grades in the program, using specific instructional routines. The words are identified as important to reading success (labeled “words to know” in their materials) because they are encountered often in print, and the fact that the words are common is referenced explicitly when teaching. For example, students are told that “You see some words many times when you read. You need to learn words that you see many times because they help you read and write (Grade 3; p. 34).”   Other properties of words, such as atypical spelling or pronunciation, are treated as secondary. The identification of atypical spelling patterns or spelling-sound correspondences is not a focus of instruction. “Discussion points” for words sometimes draw attention to parts of words or similarities between them, but these are optional. For example, for the word “because”, the “discussion points” include discussing that the word resembles “before” and “become”, or that the word “has a silent 'e' at the end”. 


```{r fp_counts_by_grade, echo=FALSE, warning=FALSE, message=FALSE}


tmp_fp = all_lists %>% 
  filter(source == 'fountas_pinnell') %>%
  mutate(order = case_when(level == "k" ~ 1,
                           level == "g1" ~ 2,
                           level == "g2" ~ 3,
                           level == "g3" ~ 4)) %>% 
  mutate(level = str_remove(level, "g"),
         level = toupper(level),
         level = fct_reorder(level, order)) %>% 
  group_by(word) %>% 
  arrange(order) %>% 
  summarise(level = first(level)) %>%
  ungroup() %>% 
  group_by(level) %>%
  summarise(n = n()) %>% 
  select(Grade = level, `F&P` =  n) %>% 
  rbind(all_lists %>% 
  filter(source == 'fountas_pinnell') %>% 
  distinct(word) %>% 
  summarise(n = n()) %>% 
  mutate(Grade = "Total") %>% 
  rename(`F&P` = n))

```


### Wonders' High-Frequency Words
The treatment of special words in the Wonders curriculum is similar to that in Fundations. The curriculum identifies a set of high frequency words that must be prioritized in instruction, many of which contain atypical structure and “cannot be decoded (Grade 1; p. S7)." There are 440 words across K-3rd grade levels (see Table 1). Words are learned through reading aloud, spelling aloud, and writing. For instructional purposes, high frequency words are organized for each year with words that share spelling patterns grouped together.   

```{r wonders_counts_by_grade, echo=FALSE, warning=FALSE, message=FALSE}

tmp_wonders = all_lists %>% 
  filter(source == 'wonders') %>% 
  mutate(order = case_when(level == "k" ~ 1,
                           level == "g1" ~ 2,
                           level == "g2" ~ 3,
                           level == "g3" ~ 4)) %>% 
  mutate(level = str_remove(level, "g"),
         level = toupper(level),
         level = fct_reorder(level, order)) %>% 
  group_by(word) %>% 
  arrange(order) %>% 
  summarise(level = first(level)) %>%
  ungroup() %>% 
  group_by(level) %>%
  summarise(n = n()) %>% 
  select(Grade = level, Wonders = n) %>% 
  rbind(all_lists %>% 
  filter(source == 'wonders') %>% 
  distinct(word) %>% 
  summarise(n = n()) %>% 
  mutate(Grade = "Total") %>% 
  rename(Wonders = n))


```

### Kilpatrick's "Irregular Words"
@Kilpatrick2016 focuses on high frequency words that violate the “grapho-phoneme regularities of printed English.” The instructional materials (Appendix I) specify a set of words that comprise “over 300 of the most common irregular words (p. 64).” The list includes many of the Dolch words, and the author states that students should be able to spell the Dolch words correctly before moving on to the remaining words.  

Kilpatrick’s approach to teaching these words is to enable readers to recognize which parts of the word are regularly or irregularly pronounced. The irregularity often arises from a single letter or letter pair; the examples provided in the text are the "ai" in "said" and the "s" in "island". With instruction the child learns to identify the irregular part (p. 58). The remainder of the word is usually regular. Here the teacher’s job is to “point out the regular elements within all words”. Learning can be enhanced by focusing the child’s attention on this part of the word, which the author terms its “phonological framework”. The child can then “use the normally performing letter-sound combinations to ‘anchor’ [the] irregular word in memory.” The text does not specify the regular and irregular elements for all of the included words, but provides examples.  

Kilpatrick also provides a second technique for teaching some of these words: Irregular words should be taught using an alternative spelling that conforms to how the word would be spelled if it had a regular pronunciation. One example provided is “Wednesday”, which should be taught with the alternative spelling “wed-ness-day”, and the regular pronunciation based on that spelling. The text notes that only some words can be taught this way, but does not indicate which ones. 



```{r Table1, echo=FALSE, message=FALSE, warning=FALSE}
tmp_fp %>%
  left_join(tmp_fundations) %>% 
  left_join(tmp_wonders) %>% 
  left_join(all_lists %>% 
  filter(source == 'fry') %>% 
  distinct(word) %>% 
  summarise(n = n()) %>% 
  mutate(Grade = "Total") %>% 
  rename(Fry = n)) %>% 
  left_join(all_lists %>% 
  filter(source == 'dolch') %>% 
  distinct(word) %>% 
  summarise(n = n()) %>% 
  mutate(Grade = "Total") %>% 
  rename(Dolch = n)) %>% 
  left_join(all_lists %>% 
  filter(source == 'kilpatrick') %>% 
  distinct(word) %>% 
  summarise(n = n()) %>% 
  mutate(Grade = "Total") %>% 
  rename(Kilpatrick = n)) %>% 
  apa_table(caption = "Number of Words in Each Instructional Source",
            note = "Number of unique words are shown. NA values indicate that the source does not specify words at the level of individual grades.", na = "--")

```



## Data Collection
The lists of special words and other information were taken from the original sources. The words are listed in tables in @Dolch1936, @Fry1980 and @Kilpatrick2016. For the remaining resources, each word taught in each unit of instruction was identified and entered in a database for analysis. This required examining instructional materials in order to extract this information about words taught (i.e., the words weren’t identified in a separate table within the resource). The resulting list is comprised of `r length(unique(all_lists$word))` unique words, and `r nrow(all_lists)` total words. Table 2 provides terms used by each program or author when referring to their special words. 

```{r Table2, echo=FALSE, message=FALSE, warning=FALSE}

tibble(Resource = c("Dolch", "Fountas & Pinnell", "Fry", "Fundations", "Kilpatrick", "Wonders"),
                Term = c('"Sight Word"', '"Word to Know"', '"Instant Word"', '"Trick Word"', '"Irregular Word"', '"High Frequency Word"')) %>% 
  apa_table(caption = "Terms for Special Words in Each Instructional Source",
            note = "See methods for descriptions of each construct and discussion of the term.")

```
