# Method
## Descriptions of Teaching Resources

We studied the words identified as requiring special instruction in six resources that are widely used in the United States: the Dolch word list [@Dolch1936; @Johns1970], the Fry word list [@Fry1980], Fundations from Wilson Language Basics [@Wilson2012], the Wonders curriculum from McGraw-Hill [@Wonders2017], the Fountas & Pinnell Comprehensive Phonics and Word Study Guide [@Fountas2018], and "Equipped for Reading Success" [@Kilpatrick2016]. These resources were selected because of their popularity at the time of conducting the study and because they address the development of early reading vocabulary, including the role of common words and the treatment of words with atypical pronunciations. Where applicable, we subset from these programs to focus on words for 3rd grade students and younger. However, @Dolch1936, @Fry1980, and @Kilpatrick2016 don't differentiate based on grade level, so we include all words provided in those resources.

The @Dolch1936 and @Fry1980 materials are list of words, originally presented in articles that described issues about learning to read and approaches to instruction. The lists, which are widely available on the internet, are utilized in research and in developing educational programs and activities. They are resources used in developing curricula but are not curricula themselves. The remaining four (Fundations, Wonders, Fountas & Pinnell's "Phonics, Spelling, & Word Study Guide" and Kilpatrick's "Equipped for Reading Success") are instructional programs in the sense that they outline both resources to use during instruction (lists of words) and methods of instruction that can be followed in delivering these resources. These four programs vary in how formal they are as instructional tools, where on one end Wonders is a large-scale comprehensive reading curriculum and at the other end @Kilpatrick2016 represents a less formal resource, delivered only as a supplementary instructional manual lacking many of the elements of more formal programs.

### Dolch "Basic Sight Vocabulary"
Dolch (1936) presented “a basic sight vocabulary” of 220 words that were considered essential for reading development because they are “...‘tool’ words that are used in all writing, no matter what the subject.” (Dolch, 1936, p. 457). This set of what are often called function words was synthesized from several previous lists and supplemented with 95 common nouns. The “Dolch list” in wide circulation usually consists of these 315 words, although sometimes with minor changes. The list includes words with both typical and atypical spelling-sound correspondences (e.g., FIVE and GIVE, respectively). Dolch recommended that the words be printed on small cards that can be “flashed” before the pupil until they can be recognized “instantly and easily.” He also noted that if the learner’s “sounding” is weak, additional training in that skill may be required. The article does not go into further detail about instruction or the process of word recognition.

### Fry "Instant Words"
@Fry1957 presented a set of 600 words consisting of high frequency words taken from word frequency lists available at the time [@Dolch1936; @Rinsland1945; @Thorndike1944] and supplemented words that the author deemed common based on personal classroom experience. The words were organized into sets of 100, ordered by frequency, and within each set into four groups of 25. The goal was to allow a reading teacher access to groups of words, decreasing in frequency, in a quantity that could be easily managed in an instructional unit. @Fry1980 introduced "The New Instant Word List", a revised version of the original set that included fewer words (300) chosen using newer frequency counts. We've included the more recent list from @Fry1980 in the analyses here.

### Wilson's Fundations "Trick Words"
The Fundations curriculum incorporates extensive instruction about systematic correspondences from spelling to sound and sound to spelling, using methods such as “tapping out” component sounds. The teacher’s manual notes that common, high frequency words need to be recognized and spelled quickly even if these correspondences have not yet be taught. These words include both “phonetically regular” and “phonetically irregular” words (i.e., words with typical and atypical mappings). The curriculum designates 193 words in K-3 as “trick” words that are to be memorized (see Table XX for the number of words per grade level). These words have irregular spelling-sound mappings according to most theories. Students are told that these words “do not follow the ‘system’ of the language…[they] are phonetically irregular”.

```{r fundations_counts_by_grade, echo=FALSE, warning=FALSE, message=FALSE}
all_lists %>% 
  filter(source == 'fundations') %>% 
  mutate(order = case_when(level == "k" ~ 1,
                           level == "g1" ~ 2,
                           level == "g2" ~ 3,
                           level == "g3" ~ 4)) %>% 
  mutate(level = str_remove(level, "g"),
         level = toupper(level),
         level = fct_reorder(level, order)) %>% 
  group_by(word) %>% 
  arrange(order) %>% 
  summarise(level = first(level)) %>%
  ungroup() %>% 
  group_by(level) %>%
  summarise(n = n()) %>% 
  select(Grade = level, n) %>% 
  apa_table(caption = "Number of Words per Grade Level from Wilson's Fundations")

```

### Fountas & Pinnell's "Words to Know"
Fountas & Pinnell's words are high-frequency words, though the origin of their lists are not specified in the program materials. These words of this kind are taught regularly throughout the elementary grades in the program, with specific instructional routines devoted to them. More specifically, these words are identified as important to reading success (labeled "words to know" in their materials) precisely because they are encountered often in print, and the fact that the words are common is referenced explicitly when teaching. For example, students are told that "You see some words many times when you read. You need to learn words that you see many times because they help you read and write." (Grade 3; p. 34) However, their structural properties are treated only as incidental; the words aren't described as exceptional other than being common. However if a given word on this list contains exceptional structure it can be pointed out by the teacher or the student. The identification of exceptional structure isn't a central aspect of what is taught to the student, and it isn't required content in the program. For example, for the word "because", a range of different possible discussion points are mentioned. These include discussing with the students that the word resembles "before" and "become", or that the word "has a silent _e_ at the end". The Fountas & Pinnell list contains 312 unique words, and their distribution across grade levels for that program are shown in Table XX.


```{r fp_counts_by_grade, echo=FALSE, warning=FALSE, message=FALSE}

all_lists %>% 
  filter(source == 'fountas_pinnell') %>%
  mutate(order = case_when(level == "k" ~ 1,
                           level == "g1" ~ 2,
                           level == "g2" ~ 3,
                           level == "g3" ~ 4)) %>% 
  mutate(level = str_remove(level, "g"),
         level = toupper(level),
         level = fct_reorder(level, order)) %>% 
  group_by(word) %>% 
  arrange(order) %>% 
  summarise(level = first(level)) %>%
  ungroup() %>% 
  group_by(level) %>%
  summarise(n = n()) %>% 
  select(Grade = level, n) %>% 
  apa_table(caption = "Number of Words per Grade Level from Fountas & Pinnell's Words to Know")

```


### Wonders' High-Frequency Words
The Wonders curriculum is similar to Wilson's Fundations in their use of special words. There is a set of very high frequency words that must be prioritized in instruction, and many of these words contain atypical structure and "cannot be decoded" (Grade 1; p. S7). There are 440 words across K-3rd grade levels (Table XX shows the number of words per level). Students are taught to read the word (including in context), spell the word aloud, and write it. The list of high-frequency words that students are exposed to throughout the year is organized based on structural properties the words contain, namely that words that contain the same spelling patterns are organized together in the list of words (organized in a visual resource in the classroom determined by the teacher), though these patterns aren't explicitly identified in the curricular materials. In general, the words are memorized using the routine that involves reading, spelling, and writing the words, though teachers are instructed to identify letter-sound structure the words contain as needed despite the structure itself not being specified in the teacher's manual.



```{r wonders_counts_by_grade, echo=FALSE, warning=FALSE, message=FALSE}

all_lists %>% 
  filter(source == 'wonders') %>% 
  mutate(order = case_when(level == "k" ~ 1,
                           level == "g1" ~ 2,
                           level == "g2" ~ 3,
                           level == "g3" ~ 4)) %>% 
  mutate(level = str_remove(level, "g"),
         level = toupper(level),
         level = fct_reorder(level, order)) %>% 
  group_by(word) %>% 
  arrange(order) %>% 
  summarise(level = first(level)) %>%
  ungroup() %>% 
  group_by(level) %>%
  summarise(n = n()) %>% 
  select(Grade = level, n) %>% 
  apa_table(caption = "Number of Words per Grade Level from Wonders Curriculum")

```

### Kilpatrick's "Irregular Words"
The "irregular words" in Kilpatrick's (2016) materials are taught on the basis that they violate the "grapho-phoneme regularities of printed English", and the text explains that they tend include many common words. The instructional materials (Appendix I) specify a set of words that comprise "over 300 of the most common irregular words to use for this activity" (p. 64). The list includes many of the Dolch wordlist, and the author states that students should be able to spell the Dolch words (included in the Appendix) correctly before moving on to the remainder of the words included. The primary technique provided for teaching these words is mnemonic: irregular words should be taught using an alternative spelling that conforms to a possible sequence of letters should the word be spelled in a more predictable fashion, and students should also be presented with the alternative pronunciation based on this alternative spelling. One example provided is "Wednesday", which should be taught with the alternative spelling of "wed-ness-day", and the associated most likely pronunciation based on that spelling^[It is noted in the text that not all irregular words permit this approach. A few examples are given for the alternative spelling/ pronunciation; an exhaustive list to support this type of instruction is not provided.]. So, as a result, the program has elements of memorization in their approach to special words, though instruction does include learning about specific segments of words that seem to violate expectations about the letter-sound relationships in English.

An additional explanation in the materials points to the utility of identifying the "irregular letter/sound connection" in an irregular word (p. 58). The author notes that irregular words are most often so because of one small segment in the word comprising the irregularity. The examples provided in the text are the AI in SAID and the S in ISLAND. Correspondingly, learning can be enhanced by focusing the child's attention on the portion of the word other than the irregularity, which the author refers to as the "phonological framework". The child then will "use the normally performing letter-sound combinations to 'anchor' [the] irregular word in memory." The teacher's job, then, is to "point out the regular elements within all words". While these segments are not exhaustively identified by the manual, the word list given in the appendix provides example words to use during instruction. Nonetheless, the critical detail to keep in mind for this instructional resource is that words are included because of their atypical structure, first and foremost. The instructional approach involves identifying the regular structure of these words support learning and subsequent retrieval. Their status as common words is secondary, but also noted.

Table XX displays the terms used by each program or author when referring to their special words.

```{r SourcesTerms, echo=FALSE, message=FALSE, warning=FALSE}

tibble(Resource = c("Dolch", "Fountas & Pinnell", "Fry", "Fundations", "Kilpatrick", "Wonders"),
                Term = c('"Sight Word"', '"Word to Know"', '"Instant Word"', '"Trick Word"', '"Irregular Word"', '"High Frequency Word"')) %>% 
  apa_table(caption = "Terms for Special Words in Each Instructional Source",
            note = "See methods for descriptions of each construct and discussion of the term.")

```

## Compiling the Wordlists
Words and other instructional data were collected for each resource. The resources were acquired through a university library system (other than the Dolch list, which is in the appendix of @Dolch1936). When identifying instructional content for each resource, teacher materials were read by a team of researchers who were supervised by a two senior researchers (the 1st and 2nd authors). Lists from @Dolch1936 and @Fry1980 were easily aggregated given that words from those publications already exist in table form in the public domain. The remaining four resources required more careful curation by the research team. For these materials, each unit of instruction was reviewed by the team and words taught in each unit were text-transcribed in a machine-readable format, and documented in a database for analysis. The resulting list is comprised of `r length(unique(all_lists$word))` unique words, and `r nrow(all_lists)` total words.


